---
title: "Introduction to ADMGs2"
author: "Robin J. Evans"
output: rmarkdown::html_vignette
date:   "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE, echo=2}
library(ADMGs2)
```

# Basics

`ADMGs2` is a package that expands `MixedGraphs` to allow for fixed vertices.  It also 
includes functions to compute intrisic sets, (recursive) heads and tails, and to fit 
models using the algorithm of Evans and Richardson (2010).  

Loading it overrides the class of vertices to include a new `fixed` class. [But for some 
reason it doesn't show up here...]
```{r vertex_types, message=FALSE}
library(ADMGs2)
vertexTypes()
```

# Making Graphs

We can create ADMGs using `graphCr()`:
```{r create_graph}
gr <- graphCr("1 -> 2 <-> 4 <- 3")
```
To create a CADMG, we just need to fix a vertex.
```{r fix_node}
fix(gr, 3)
```


## References

Evans, R.J. and Richardson, T.S.  Maximum likelihood fitting of acyclic directed mixed graphs to binary data, _UAI-10_, 2010.